Stateless Model Checking with Data-Race Preemption Points

### 2015-10-13 pldi-16/paper.tex
get average LOC of p2s
random stuff

% TODO: Don't forget to run e.g. s/\\quicksand /\\quicksand~/
\newcommand\landslide{\textsc{Landslide}}
\newcommand\quicksand{\textsc{Quicksand}}

% TODO: Finalize these numbers.
\newcommand\numthrlibs{{\Large \bf NUMP2S}}
\newcommand\numpintoses{{\Large \bf NUMPINTOSES}}
\newcommand\numstudence{{\Large \bf NUMSTUDENCE}} % total pintoses plus p2s

@@

We are
%overwhelmingly
great. Accept our paper.

@@

Although \landslide~itself is not publicly available due to its dependency on the non-free simulator {\sc Simics}, \quicksand~is open-source and its interface can be adapted to fit any similar tool.
We have also posted the log files from all our experiments.
They can be found here:

@@

Many thanks to David A. Eckhardt, Vaishaal Shankar, and Haryadi Gunawi for generously providing student implementations from CMU's, Berkeley's, and U. of Chicago's OS classes respectively.
Thanks to Wind River Simics for %TODO
Thanks to Ji\v{r}\'{i} \v{S}im\v{s}a and the anonymous PLDI reviewers for their helpful comments.
This work was supported in part by % TODO: funding sources

>>>>

% TODO: Don't forget to run e.g. s/\\quicksand /\\quicksand~/
\newcommand\landslide{\textsc{Landslide}}
\newcommand\quicksand{\textsc{Quicksand}}
\newcommand\simics{\textsc{Simics}}

% TODO: Finalize these numbers.
\newcommand\numthrlibs{79}
\newcommand\numpintoses{{\Large \bf NUMPINTOSES}}
\newcommand\numstudence{{\Large \bf NUMSTUDENCE}} % total pintoses plus p2s

@@

%We are great. Accept our paper.

@@

Although \landslide~itself is not publicly available due to its dependency on the non-free simulator \simics, \quicksand~is open-source and its interface can be adapted to fit any similar tool.
We have also posted the log files from all our experiments.
They can be found here:

@@

Many thanks to David A. Eckhardt, Vaishaal Shankar, and Haryadi Gunawi for generously providing student implementations from CMU's, Berkeley's, and U. of Chicago's OS classes respectively.
Thanks to Wind River for the use of their simulator \simics, upon which \landslide~is built.
Thanks to Ji\v{r}\'{i} \v{S}im\v{s}a and the anonymous PLDI reviewers for their helpful comments.
This work was supported in part by % TODO: funding sources

### 2015-10-13 pldi-16/related.tex
random stuff

@@

{\bf Preempting at instruction granularity} is a prerequisite for using data-race PPs. However, every such prior tool we know of has serious drawbacks.
{\textsc SKI} \cite{ski} approaches kernel code by choosing in advance a random set of instruction offsets from the start of the test,
which is more similar to stress testing or fuzzing than to exhaustive state space exploration.
% TODO: Make sure you talk about your mutex experiment, or rephrase this.
SPIN \cite{spin} specializes in verifying synchronization primitive implementations such as RCU, which is very similar to our mutex-testing experiment.
However, it does not employ Iterative Deepening, and requires programs to be written in the PROMELA DSL, so cannot check implementations directly.

@@

>>>>

\subsection{Stateless Model Checking}

@@

{\bf Preempting at instruction granularity} is a prerequisite for using data-race PPs. However, every such prior tool we know of has serious drawbacks.
{\textsc SKI} \cite{ski} approaches kernel code by choosing in advance a random set of instruction offsets from the start of the test,
which is more similar to stress testing or fuzzing than to exhaustive state space exploration.
% TODO: Make sure you talk about your mutex experiment, or rephrase this.
SPIN \cite{spin} specializes in verifying synchronization primitive implementations such as RCU, which is very similar to our \mxtest~experiment.
However, it does not employ Iterative Deepening, and requires programs to be written in the PROMELA DSL, so cannot check implementations directly.

@@

\subsection{Data Race Detection}

blah blah blah eraser

blah blah blah threadsanitizer, racePRO, etc

\subsection{Other Concurrency Testing Approaches} % TODO: Well?

blah blah pldi'15 symbiosis DSP
